% vision ?
\section{Our Ambition: Provide the High-Performance Computing Platform for the Most Demanding Applications.}

%% ── NEW: Introduction frames (5 frames) ──

% Frame 1: FSI World
\begin{frame}{The FSI World}
	\begin{columns}[T]
		\begin{column}{0.42\textwidth}
			\centering\vspace{0.3cm}
			\begin{tikzpicture}[
					box/.style={rectangle, rounded corners=4pt, font=\footnotesize\bfseries,
							minimum width=3.6cm, minimum height=0.7cm, align=center, text=white},
					arr/.style={-Stealth, thick, aneoorange!80}
				]
				\node[box, fill=aneoblue] (ep) at (0, 0)
					{Embarrassingly\\Parallel\\(Monte Carlo)};
				\draw[arr] (ep.south) -- ++(0,-0.4);
				\node[box, fill=aneoorange] (cx) at (0, -1.8)
					{Complex Nested\\Algorithms\\(XVA, AAD)};
				\draw[arr] (cx.south) -- ++(0,-0.4);
				\node[box, fill=aneoorange!20, draw=aneoorange!60, text=aneoblack,
						font=\tiny, minimum height=1.0cm] (lp) at (0, -3.5)
					{Lost Properties\\Fault tolerance\\Malleability\\Cloud portability};
			\end{tikzpicture}
		\end{column}
		\begin{column}{0.58\textwidth}
			\vspace{0.5cm}
			\begin{itemize}
				\item \textbf{HTC schedulers} powered embarrassingly parallel Monte Carlo in production
				\item \textbf{XVA/CVA \& AAD} introduced portfolio-level aggregation and backward graph traversal
				\item \textbf{Complex setups} emerged to integrate algorithm complexity within orchestration
				\item \textbf{Fault tolerance, malleability, cloud portability} — originally free with HTC — became harder to maintain
			\end{itemize}
		\end{column}
	\end{columns}

	\note{
		\begin{itemize}
			\item The FSI world started simple: Monte Carlo simulations are embarrassingly
			      parallel — you throw thousands of independent paths at an HTC scheduler
			      and collect results. Fault tolerance and malleability came for free because
			      every task was independent.
			\item Then quant algorithms got more sophisticated. XVA and CVA adjustments
			      require portfolio-level aggregation across counterparties. Adjoint
			      Algorithmic Differentiation computes Greeks by traversing the computation
			      graph backward. These aren't embarrassingly parallel anymore — they have
			      deep, nested dependencies.
			\item Some teams built incredibly complex setups — custom orchestration layers
			      bolted onto HTC schedulers — to handle this new complexity. But the
			      properties they used to get for free (fault tolerance, malleability,
			      easy cloud migration) started slipping away. That's the tension this
			      world was living with.
		\end{itemize}
	}
\end{frame}

%% ── END: Frame 1 ──

% Frame 2: HPC World
\begin{frame}{The HPC World}
	\begin{columns}[T]
		\begin{column}{0.52\textwidth}
			\vspace{0.5cm}
			\begin{itemize}
				\item \textbf{Supercomputer workloads} with complex node-to-node communication patterns
				\item \textbf{MPI} enables performance but is complex and hard to reason about correctly
				\item \textbf{Fault tolerance \& malleability} are difficult to achieve with MPI's rigid model
				\item \textbf{Hardware adaptation} (changing node counts at launch) is often painful
			\end{itemize}
		\end{column}
		\begin{column}{0.48\textwidth}
			\centering\vspace{0.3cm}
			\begin{tikzpicture}[
					mpibox/.style={rectangle, rounded corners=4pt, fill=aneoblue!15,
							draw=aneoblue!40, text=aneoblack, font=\footnotesize\bfseries,
							minimum width=2.2cm, minimum height=1.8cm, align=center},
					taskbox/.style={rectangle, rounded corners=4pt, fill=aneoturquoise!20,
							draw=aneoturquoise!50, text=aneoblack, font=\footnotesize\bfseries,
							minimum width=3.0cm, minimum height=1.8cm, align=center},
					arr/.style={-Stealth, thick, aneoorange, dashed}
				]
				\node[mpibox] (mpi) at (0, 0) {MPI\\Rigid\\Model};
				\node[taskbox] (tbr) at (4.2, 0) {Task-Based\\Runtimes\\[4pt]
					{\tiny StarPU, PaRSEC}\\[-1pt]
					{\tiny Legion, OmpSs}\\[-1pt]
					{\tiny Charm++}};
				\draw[arr] (mpi.east) -- (tbr.west)
					node[midway, above, font=\tiny\itshape, text=aneoorange] {manytask}
					node[midway, below, font=\tiny\itshape, text=aneoorange] {computing};
			\end{tikzpicture}
		\end{column}
	\end{columns}

	\note{
		\begin{itemize}
			\item In the traditional HPC world, algorithms are designed for supercomputers
			      with tightly coupled nodes communicating via MPI. These workloads lack
			      the data parallelism that makes embarrassingly parallel approaches work.
			\item MPI is powerful but unforgiving. Getting the communication patterns right
			      is hard, debugging is harder, and if a single node fails, the entire
			      computation typically has to restart. Malleability — dynamically adjusting
			      the number of nodes at runtime — is essentially impossible with standard
			      MPI.
			\item The HPC community recognized these limitations and started building
			      task-based runtimes: StarPU, PaRSEC, Legion, OmpSs, Charm++. These
			      frameworks decompose computations into tasks with explicit dependencies,
			      letting the runtime handle scheduling, fault recovery, and hardware
			      adaptation. This is the HPC world's own path toward the same abstraction
			      we'll see from the other two worlds.
		\end{itemize}
	}
\end{frame}

%% ── END: Frame 2 ──

% Frame 3: Cloud Computing World
\begin{frame}{The Cloud Computing World}
	\begin{columns}[T]
		\begin{column}{0.45\textwidth}
			\centering\vspace{0.3cm}
			\begin{tikzpicture}
				\node[rectangle, rounded corners=5pt, fill=aneoturquoise!15,
					draw=aneoturquoise!40, text=aneoblack, text width=4.0cm,
					align=left, inner sep=8pt, minimum height=2.8cm] (promise) at (0,0) {%
					{\footnotesize\bfseries\color{aneoturquoise!80!black}Compelling Model}\\[4pt]
					{\small\color{aneoblack}%
					\begin{itemize}\setlength{\itemsep}{1pt}
						\item[\textbullet] Elasticity
						\item[\textbullet] Virtually unlimited resources
						\item[\textbullet] Pay-per-use pricing
						\item[\textbullet] Spot/preemptible instances
					\end{itemize}}%
				};
			\end{tikzpicture}
		\end{column}
		\begin{column}{0.55\textwidth}
			\centering\vspace{0.3cm}
			\begin{tikzpicture}
				\node[rectangle, rounded corners=5pt, fill=aneoorange!15,
					draw=aneoorange!40, text=aneoblack, text width=4.6cm,
					align=left, inner sep=8pt, minimum height=2.8cm] (complex) at (0,0) {%
					{\footnotesize\bfseries\color{aneoorange!80!black}New Complexities}\\[4pt]
					{\small\color{aneoblack}%
					\begin{itemize}\setlength{\itemsep}{1pt}
						\item[\textbullet] Malleability \& fault tolerance
						\item[\textbullet] Data movement \& lifecycle
						\item[\textbullet] Multi-tenancy \& security
						\item[\textbullet] Latency, portability \& cost
					\end{itemize}}%
				};
			\end{tikzpicture}
		\end{column}
	\end{columns}

	\vspace{0.2cm}
	\centering{\small\itshape\color{aneoblack!60}
		These complexities demand a higher-level execution abstraction.}

	\note{
		\begin{itemize}
			\item I started the HPC cloud adventure back in 2012, building a first
			      Azure-focused scheduling layer. The cloud promise was — and still is —
			      incredibly compelling: elastic resources, pay only for what you use,
			      and spot instances that can slash costs by 60-90\%.
			\item But leveraging that model properly opened a Pandora's box. Your code
			      needs to handle changing resource counts at runtime — that's malleability.
			      Spot instances can be reclaimed at any moment — that's fault tolerance.
			      Data is no longer on a shared filesystem — you need to manage data
			      movements, replication, and cleanup across distributed storage.
			\item There's also multi-tenancy, network latency compared to on-prem
			      interconnects, hardware portability across CPU/GPU/ARM, and cost
			      optimization. And here's one that security teams care deeply about:
			      legacy schedulers typically require inbound connections from the cloud
			      to on-premises networks. Enterprise security teams reject that outright.
			      ArmoniK was specifically designed with outbound-only connections from
			      on-prem to cloud, eliminating that blocker.
			\item The key insight is that all these complexities shouldn't be the
			      application developer's problem. They need a higher-level abstraction
			      that handles this for them.
		\end{itemize}
	}
\end{frame}

%% ── END: Frame 3 ──

% Frame 4: Convergence
\begin{frame}{Three Worlds, One Abstraction}
	\centering\vspace{0.1cm}
	\begin{tikzpicture}[
			src/.style={rectangle, rounded corners=5pt, minimum width=3.8cm,
					text width=3.4cm, minimum height=1.0cm, font=\small\bfseries, align=center},
			arr/.style={-Stealth, thick}
		]
		% Source nodes (left) — examples included in each node
		\node[src, fill=aneoblue!15, draw=aneoblue!40, text=aneoblue]
			(fsi) at (0, 1.4) {FSI World\\[1pt]{\tiny\color{aneoblack!70}Dask, Symphony, DataSynapse}};
		\node[src, fill=aneoturquoise!15, draw=aneoturquoise!40, text=aneoturquoise!80!black]
			(hpc) at (0, 0) {HPC World\\[1pt]{\tiny\color{aneoblack!70}StarPU, PaRSEC, Legion, Charm++}};
		\node[src, fill=aneoorange!15, draw=aneoorange!40, text=aneoorange!80!black]
			(cloud) at (0, -1.4) {Cloud World\\[1pt]{\tiny\color{aneoblack!70}Airflow, Step Functions, Ray, Dask}};

		% Central node (right) — same width, tall enough to span all three source nodes
		\node[src, rounded corners=6pt, fill=aneoblue, text=white,
			font=\normalsize\bfseries, minimum height=3.8cm] (dag) at (5.5, 0)
			{DAG of Tasks\\[2pt]{\tiny Decouple algorithm from execution}};

		% Convergence arrows — each hits the DAG box edge at source height
		\draw[arr, aneoblue!70]       (fsi.east)   -- (dag.west |- fsi);
		\draw[arr, aneoturquoise!70]  (hpc.east)   -- (dag.west);
		\draw[arr, aneoorange!70]     (cloud.east) -- (dag.west |- cloud);

	\end{tikzpicture}

	\note{
		\begin{itemize}
			\item Here's the punchline: all three worlds — independently, without
			      coordinating — arrived at the same fundamental abstraction. Directed
			      acyclic graphs of tasks.
			\item In FSI, tools like Dask and proprietary platforms like Symphony and
			      DataSynapse moved toward expressing computations as task graphs. In
			      HPC, StarPU, PaRSEC, Legion, and Charm++ all decompose algorithms
			      into tasks with explicit data dependencies. In cloud, Airflow, AWS
			      Step Functions, and Ray all orchestrate DAGs of work.
			\item Why DAGs? Because they decouple the algorithm's structure from how
			      and where it executes. Once you have a DAG, the runtime can handle
			      fault tolerance (re-run failed nodes), malleability (schedule across
			      changing resources), and portability (run the same graph on-prem or
			      in the cloud).
			\item ArmoniK's insight was to go further. Instead of a plain DAG of tasks,
			      ArmoniK uses a bipartite DAG — with both task nodes and data nodes as
			      first-class citizens. This means data isn't just an implicit side
			      effect of task execution; it's an explicit node in the graph. That
			      enables data-aware scheduling, explicit data lifecycle management,
			      and computation-communication overlapping. We'll see this in detail
			      shortly.
		\end{itemize}
	}
\end{frame}

%% ── END: Frame 4 ──

% Frames 4a–4b: Dynamic Graphs (single frame, two overlays)
\begin{frame}<1-2>{Dynamic Graphs can Fully Describe Complex Algorithms}
	\centering\vspace{0.1cm}
	\begin{tikzpicture}[
			% ── shared styles ──
			data/.style={rectangle, rounded corners=3pt, fill=aneoblue!18,
				draw=aneoblue!50, text=aneoblack, font=\footnotesize\bfseries,
				minimum width=1.5cm, minimum height=0.55cm, align=center},
			task/.style={rectangle, rounded corners=10pt, fill=aneoorange!25,
				draw=aneoorange!60, text=aneoblack, font=\footnotesize\bfseries,
				minimum width=1.5cm, minimum height=0.55cm, align=center},
			result/.style={rectangle, rounded corners=3pt, fill=aneoblue!30,
				draw=aneoblue!60, text=aneoblack, font=\footnotesize\bfseries,
				minimum width=1.5cm, minimum height=0.55cm, align=center},
			smalldata/.style={rectangle, rounded corners=2pt, fill=aneoblue!18,
				draw=aneoblue!50, text=aneoblack, font=\tiny\bfseries,
				minimum width=1.1cm, minimum height=0.45cm, align=center},
			smalltask/.style={rectangle, rounded corners=8pt, fill=aneoorange!25,
				draw=aneoorange!60, text=aneoblack, font=\tiny\bfseries,
				minimum width=1.1cm, minimum height=0.45cm, align=center},
			smallresult/.style={rectangle, rounded corners=2pt, fill=aneoblue!30,
				draw=aneoblue!60, text=aneoblack, font=\tiny\bfseries,
				minimum width=1.3cm, minimum height=0.55cm, align=center},
			arr/.style={-Stealth, thick, aneoblue!70},
			sarr/.style={-Stealth, thin, aneoorange!70},
			userarr/.style={-Stealth, thick, aneoblue},
			lab/.style={font=\tiny\itshape, text=aneoblack!70, align=left}
		]
		% Fix bounding box first (invisible)
		\useasboundingbox (-5.8, -4.0) rectangle (9.8, 3.2);

		% ════════════════════════════════════════════
		%  Shared elements (both overlays)
		% ════════════════════════════════════════════

		% Data nodes + background box
		\node[data] (d1) at (0.0, 2.2) {Data 1};
		\node[data] (d2) at (1.8, 2.2) {Data 2};

		% Solve task
		\node[task] (solve) at (0.9, 0.9) {Solve};

		% Result
		\node[result] (res) at (0.9, -3.3) {Result};

		% Data → Solve arrows
		\draw[arr] (d1.south) -- (solve.north);
		\draw[arr] (d2.south) -- (solve.north);

		% ── Developer icon (stick figure, no circle head, no code symbol) ──
		% Placed far left; arrows will start from explicit coordinates to the right
		\begin{scope}[shift={(-4.8, 0.0)}, scale=1.1]
			% Head (filled, no separate stroke circle)
			\fill[aneoblack!60] (0, 0.6) circle (0.18);
			% Body
			\draw[semithick, aneoblack!60] (0, 0.42) -- (0, -0.05);
			% Arms
			\draw[semithick, aneoblack!60] (-0.28, 0.2) -- (0, 0.32) -- (0.28, 0.2);
			% Legs
			\draw[semithick, aneoblack!60] (0, -0.05) -- (-0.2, -0.42);
			\draw[semithick, aneoblack!60] (0, -0.05) -- (0.2, -0.42);
		\end{scope}

		% Arrow origins — to the right of the figure, so arrows don't overlap it
		\coordinate (arrowstart) at (-4.2, 0.0);

		% User interaction arrows
		\draw[userarr] (arrowstart |- 0,0.5) -- (d1.west)
			node[pos=0.35, above, lab] {1. User provides data};
		\draw[userarr] (arrowstart) -- (solve.west)
			node[pos=0.4, above, lab] {2. User submits\\the task};
		\draw[userarr] (arrowstart |- 0,-0.5) -- (res.west)
			node[pos=0.3, below, lab] {3. User waits for the result\\availability and downloads\\the result};

		% ════════════════════════════════════════════
		%  Overlay 1 only: simple direct arrow Solve → Result
		% ════════════════════════════════════════════
		\only<1>{%
			\draw[arr] (solve.south) -- (res.north);
		}

		% ════════════════════════════════════════════
		%  Overlay 2 only: dynamic subgraph
		% ════════════════════════════════════════════
		\only<2>{%
			% Solve → Result (delegated, still present)
			\draw[arr] (solve.south) -- (res.north);

			% Subgraph background box
			\node[draw=aneoblue!25, fill=aneoblue!8, rounded corners=6pt,
				inner sep=0pt, minimum width=6.2cm, minimum height=5.6cm]
				(subbox) at (6.6, -0.5) {};

			% Step 4 label
			\node[lab, text=aneoblack!80] at (3.3, 0.5)
				{4. Solver submits\\subgraph and\\delegates result\\production};
			\draw[userarr, aneoorange!80] (solve.east) -- (3.8, 0.5);

			% ── Sub-data nodes (with stacked-copy effect) ──
			\foreach \i/\xpos/\lbl in {3/4.6/Data 3, 4/5.8/Data 4, 5/7.0/Data 5, 6/8.2/Data 6}{
				\node[smalldata, yshift=4pt, xshift=2pt, opacity=0.2] at (\xpos, 1.8) {};
				\node[smalldata, yshift=2pt, xshift=1pt, opacity=0.4] at (\xpos, 1.8) {};
				\node[smalldata] (sd\i) at (\xpos, 1.8) {\lbl};
			}

			% Data 2 → sub-data (dashed fan-out, curving above the subgraph)
			\draw[arr, dashed] (d2.east) .. controls +(1.5,0.8) and +(-0.5,0.8) .. (sd3.north);
			\draw[arr, dashed] (d2.east) .. controls +(2.5,1.0) and +(-0.3,0.8) .. (sd4.north);
			\draw[arr, dashed] (d2.east) .. controls +(3.5,1.0) and +( 0.0,0.8) .. (sd5.north);
			\draw[arr, dashed] (d2.east) .. controls +(4.5,1.0) and +( 0.3,0.8) .. (sd6.north);

			% ── Sub-solve tasks (3 solvers, spaced to match data pairs) ──
			\node[smalltask] (ss1) at (5.2, 0.4) {Solve};
			\node[smalltask] (ss2) at (6.4, 0.4) {Solve};
			\node[smalltask] (ss3) at (7.6, 0.4) {Solve};

			% Data → Solve arrows (each solver gets 2 adjacent data nodes)
			\draw[sarr] (sd3.south) -- (ss1.north);
			\draw[sarr] (sd4.south) -- (ss1.north);
			\draw[sarr] (sd4.south) -- (ss2.north);
			\draw[sarr] (sd5.south) -- (ss2.north);
			\draw[sarr] (sd5.south) -- (ss3.north);
			\draw[sarr] (sd6.south) -- (ss3.north);

			% ── Intermediate results ──
			\node[smallresult] (ir1) at (5.2, -0.9) {Intermediate\\[-1pt]Result};
			\node[smallresult] (ir2) at (6.4, -0.9) {Intermediate\\[-1pt]Result};
			\node[smallresult] (ir3) at (7.6, -0.9) {Intermediate\\[-1pt]Result};

			\draw[sarr] (ss1.south) -- (ir1.north);
			\draw[sarr] (ss2.south) -- (ir2.north);
			\draw[sarr] (ss3.south) -- (ir3.north);

			% ── Aggregate ──
			\node[task, font=\footnotesize\bfseries] (agg) at (6.4, -2.2) {Aggregate};

			\draw[sarr] (ir1.south) -- (agg.north west);
			\draw[sarr] (ir2.south) -- (agg.north);
			\draw[sarr] (ir3.south) -- (agg.north east);

			% Aggregate → Result (curves left to the shared Result node)
			\draw[arr] (agg.south) .. controls +(0,-0.6) and +(3.5,0) .. (res.east);
		}
	\end{tikzpicture}

	\note<1>{
		\begin{itemize}
			\item This is the simplest view of a compute workflow in ArmoniK.
			      The user uploads input data, submits a single Solve task that
			      depends on that data, and waits for the result.
			\item From the user's perspective, this looks like a simple
			      request-response pattern. But the key insight is that the
			      Solve task itself can dynamically modify the execution graph
			      at runtime — which is what we'll see on the next slide.
			\item This is a real FSI pattern: a quant library receives market
			      data and model parameters, then decides internally how to
			      decompose the computation.
		\end{itemize}
	}
	\note<2>{
		\begin{itemize}
			\item This is where dynamic graphs shine. The Solve task, at runtime,
			      inspects the input data and decides it needs to decompose the
			      problem further. It submits an entire subgraph: new data partitions,
			      parallel Solve tasks, intermediate results, and an Aggregate step.
			\item The compute library — not the orchestrator, not the user — makes
			      this decision dynamically. The graph evolves based on actual data
			      characteristics: data size, convergence criteria, model complexity.
			\item This is a real FSI pattern. A pricing library receives a portfolio
			      and decides to split it by counterparty, run XVA adjustments in
			      parallel, then aggregate. The decomposition strategy depends on the
			      portfolio contents — it cannot be known at submission time.
			\item ArmoniK handles this natively: the Solve task submits child tasks
			      and data nodes, delegates result production to the Aggregate task,
			      and the platform manages scheduling, fault tolerance, and data
			      lifecycle for the entire dynamically-created subgraph.
		\end{itemize}
	}
\end{frame}

%% ── END: Frames 4a–4b ──

% Frame 5: Positioning
\begin{frame}{ArmoniK}
	\begin{alertblock}{What is ArmoniK?}
		A production-ready, bipartite-DAG task orchestrator for critical environments
		— making it easy to develop, observe, and operate distributed algorithms.
	\end{alertblock}

	\vspace{0.1cm}
	\centering
	\begin{tikzpicture}[
			card/.style={rectangle, rounded corners=5pt, text width=5.4cm,
					align=left, inner sep=6pt, minimum width=5.8cm, minimum height=1.6cm}
		]
		\node[card, fill=aneoblue!12, draw=aneoblue!35] at (0, 0) {%
		{\footnotesize\bfseries\color{aneoblue}Industry-Grade Scalability}\\[2pt]
		{\tiny\color{aneoblack}Production-ready, high-throughput platform hardened in financial services \& critical environments}%
		};
		\node[card, fill=aneoturquoise!15, draw=aneoturquoise!40] at (6.2, 0) {%
		{\footnotesize\bfseries\color{aneoturquoise!80!black}HPC Performance Techniques}\\[2pt]
		{\tiny\color{aneoblack}Computation-communication overlapping, pipelining, and future HPC optimizations}%
		};
		\node[card, fill=aneoorange!12, draw=aneoorange!35] at (0, -2.0) {%
		{\footnotesize\bfseries\color{aneoorange!80!black}Developer-Centric \& Observable}\\[2pt]
		{\tiny\color{aneoblack}Easy to use — rich APIs for observability, extensibility \& integration; focus on algorithms, not infra}%
		};
		\node[card, fill=aneoblue!8, draw=aneoblue!25] at (6.2, -2.0) {%
		{\footnotesize\bfseries\color{aneoblue!70!black}Dynamic Bipartite DAG}\\[2pt]
		{\tiny\color{aneoblack}Data as first-class graph citizens; DAG evolves at runtime based on data \& intermediate results}%
		};
	\end{tikzpicture}

	\vspace{0.15cm}
	\centering{\tiny\color{aneoblack!50} Open source — Apache 2.0 License}

	\note{
		\begin{itemize}
			\item So what is ArmoniK? It's a task orchestrator built on a bipartite DAG
			      model — tasks and data are both first-class nodes in the execution
			      graph. This isn't just an academic distinction; it's what enables
			      data-aware scheduling and explicit data lifecycle management.
			      Crucially, ArmoniK supports dynamic DAGs: the graph can be modified
			      during execution, allowing algorithms whose structure depends on
			      actual data and intermediate results — not just a static plan
			      defined upfront.
			\item ArmoniK targets critical, mission-critical applications — risk systems,
			      regulatory computations, production trading systems. These are
			      applications that absolutely cannot fail in production. Yet our
			      developer-centric design means building these systems doesn't require
			      infrastructure expertise. ArmoniK's mission is to ease using computing
			      resources and ease the development of complex distributed algorithms.
			\item The FSI-grade scalability comes from being battle-tested in financial
			      services — high-throughput, production-hardened. The HPC performance
			      techniques — computation-communication overlapping and pipelining —
			      come from applying lessons learned in the HPC world, with plans to
			      leverage additional techniques in the future.
			\item And it's fully open source under the Apache 2.0 license. You can
			      inspect, modify, and deploy it without vendor lock-in.
		\end{itemize}
	}
\end{frame}

%% ── END: Frame 5 ──
%% ── END: Introduction frames ──

% \begin{frame}{ArmoniK's envisioned capabilities}
% 	\vspace{0.15cm}\centering
% 	\begin{tikzpicture}[
% 			b/.style={rectangle, rounded corners=4pt, fill=aneoblue, text=white,
% 					font=\small\bfseries, minimum width=5.0cm, minimum height=0.75cm,
% 					align=center},
% 			bo/.style={b, fill=aneoorange, text=aneoblack}
% 		]
% 		\node[b]  at (0, 0.00) {Production Ready};
% 		\node[b]  at (0,-0.95) {Fault Tolerant};
% 		\node[b]  at (0,-1.90) {Malleable};
% 		\node[bo] at (0,-2.85) {Data Aware};
% 		\node[bo] at (0,-3.80) {Smart Scheduling};
% 		\node[b]  at (5.4, 0.00) {Easy to Use \& Deploy};
% 		\node[b]  at (5.4,-0.95) {Observable};
% 		\node[b]  at (5.4,-1.90) {Portable};
% 		\node[b]  at (5.4,-2.85) {Performant};
% 		\node[b]  at (5.4,-3.80) {Open Source};

% 		% Legend
% 		\node[b,   minimum width=0.75cm, minimum height=0.45cm] at (0.80, -4.65) {};
% 		\node[anchor=west, font=\tiny, text=aneoblack] at (1.25, -4.65) {Foundation capabilities};
% 		\node[bo,  minimum width=0.75cm, minimum height=0.45cm] at (4.40, -4.65) {};
% 		\node[anchor=west, font=\tiny, text=aneoblack] at (4.85, -4.65) {Key differentiators};
% 	\end{tikzpicture}

% 	\note
% 	{
% 		\begin{itemize}
% 			\item \textbf{Production ready}, with support for security, scalability, and reliability.
% 			\item \textbf{Easy to use and deploy}, with a user-friendly interface and comprehensive documentation.
% 			\item \textbf{Fault tolerant}, with support for automatic recovery and rescheduling of failed tasks.
% 			\item \textbf{Observable}, with support for monitoring and logging of task execution.
% 			\item \textbf{Malleable}, with support for dynamic resource allocation.
% 			\item \textbf{Portable}, with support for multiple platforms and cloud providers.
% 			\item \textbf{Data aware}, with support for data locality and efficient data management.
% 			\item \textbf{Performant}, with support for high-throughput and high-volume task execution.
% 			\item \textbf{Smart scheduling}, with priority, preemption, and heterogeneous resource placement.
% 			\item \textbf{Open source}, with a vibrant community of users and contributors.
% 		\end{itemize}
% 	}

% \end{frame}


% \begin{frame}{Production Ready}
% 	\centering\vspace{0.2cm}
% 	\begin{tikzpicture}[
% 			card/.style={rectangle, rounded corners=5pt, text width=4.8cm,
% 					align=left, inner sep=8pt, minimum width=5.5cm, minimum height=2.4cm}
% 		]
% 		\node[card, fill=aneoblue!12, draw=aneoblue!35] at (0, 0) {%
% 		{\footnotesize\bfseries\color{aneoblue}Security}\\[3pt]
% 		{\tiny\color{aneoblack}• Strict separation of Control, Data, and Compute Planes}\\[1pt]
% 		{\tiny\color{aneoblack}• Encryption at rest and in transit}\\[1pt]
% 		{\tiny\color{aneoblack}• Secure secret injection for workers}%
% 		};
% 		\node[card, fill=aneoturquoise!15, draw=aneoturquoise!40] at (6.0, 0) {%
% 		{\footnotesize\bfseries\color{aneoturquoise!80!black}Reliability}\\[3pt]
% 		{\tiny\color{aneoblack}• No single point of failure, automated failover}\\[1pt]
% 		{\tiny\color{aneoblack}• Idempotent operations with well-defined state transitions}\\[1pt]
% 		{\tiny\color{aneoblack}• Robust error handling under retries and failures}%
% 		};
% 		\node[card, fill=aneoorange!12, draw=aneoorange!35] at (0, -2.9) {%
% 		{\footnotesize\bfseries\color{aneoorange!80!black}Scalability}\\[3pt]
% 		{\tiny\color{aneoblack}• Stateless components scale out under high concurrency}\\[1pt]
% 		{\tiny\color{aneoblack}• Predictable behaviour at production scale}\\[1pt]
% 		{\tiny\color{aneoblack}• Rate limiting and throttling per tenant}%
% 		};
% 		\node[card, fill=aneoblue!8, draw=aneoblue!25] at (6.0, -2.9) {%
% 		{\footnotesize\bfseries\color{aneoblue!70!black}Enterprise}\\[3pt]
% 		{\tiny\color{aneoblack}• Tenant isolation, per-tenant quotas, noisy-neighbor prevention}\\[1pt]
% 		{\tiny\color{aneoblack}• Identity integration and role separation}\\[1pt]
% 		{\tiny\color{aneoblack}• Auditability and governance}%
% 		};
% 	\end{tikzpicture}

% 	\note
% 	{
% 		\begin{itemize}
% 			\item \textbf{Security by Architecture:} Strict separation of Control, Data, and Compute Planes
% 			\item \textbf{Data Protection:} Encryption at rest and in transit, secure secret injection for workers
% 			\item \textbf{High Availability:} No single point of failure, automated failover and recovery
% 			\item \textbf{Horizontal Scalability:} Stateless components scale out under high concurrency
% 			\item \textbf{Robust Error Handling:} Idempotent operations with well-defined state transitions
% 			\item \textbf{Multi-Tenancy:} Tenant isolation, per-tenant quotas, and noisy-neighbor prevention
% 			\item \textbf{Enterprise Governance:} Identity integration, role separation, and auditability
% 		\end{itemize}
% 	}
% \end{frame}

\begin{frame}{Easy to Use \& Deploy}
	\begin{itemize}
		\item \textbf{Flexible Deployment:} From fully managed to self-operated
		\item \textbf{Low-Friction Onboarding:} Automated provisioning and standardized configurations
		\item \textbf{Declarative Configuration:} Repeatable, auditable, drift-free deployments
		\item \textbf{Developer-Centric SDKs:} Multi-language APIs that abstract orchestration complexity
		\item \textbf{Local Dev \& Test:} Run and debug tasks locally before deploying to the cluster
		\item \textbf{Worker Versioning:} Canary rollouts, rollback, and side-by-side version coexistence
		\item \textbf{Reduced Operational Burden:} Clear responsibilities and comprehensive documentation
	\end{itemize}
\end{frame}

\begin{frame}{Fault Tolerant}
	\begin{columns}[T]
		\begin{column}{0.52\textwidth}
			\begin{figure}
				\centering\vspace{0.3cm}
				\begin{tikzpicture}[
						st/.style={rectangle, rounded corners=4pt, font=\footnotesize\bfseries,
								minimum width=1.8cm, minimum height=0.6cm, align=center},
						ok/.style={st, fill=aneoturquoise!30, draw=aneoturquoise!70, text=aneoblack},
						fail/.style={st, fill=aneoorange!25, draw=aneoorange!80, text=aneoblack},
						arr/.style={-Stealth, thick},
						lab/.style={font=\tiny\itshape, text=aneoblack!60}
					]
					\node[ok]   (run)  at (0,0)      {Running};
					\node[fail] (fail) at (3.2,0)    {Failed};
					\node[ok]   (sch)  at (1.6,-1.6) {Rescheduled};

					\draw[arr, aneoblue!70] (-1.6,0) -- (run.west)
					node[midway, above, lab] {submitted};
					\draw[arr, aneoorange!90] (run.east) -- (fail.west)
					node[midway, above, lab, text=aneoorange!80] {failure};
					\draw[arr, aneoorange!90] (fail.south) -- (sch.east)
					node[midway, right, lab] {detected};
					\draw[arr, aneoblue!70] (sch.west) -- (run.south)
					node[midway, left, lab] {retry};
				\end{tikzpicture}
				\caption*{Automatic Recovery}
			\end{figure}
		\end{column}
		\begin{column}{0.48\textwidth}
			\vspace{0.5cm}
			\begin{itemize}
				\item \textbf{Checkpointing:} Persist task state for efficient resumption
				\item \textbf{Failure Isolation:} Failures contained to domains (clusters, partitions, workers) without cascading effects
				\item \textbf{Idempotent Operations:} Safe retries with consistent outcomes
				\item \textbf{Graceful Degradation:} Services restart without impact on running workloads
			\end{itemize}
		\end{column}
	\end{columns}

	\note
	{
		\begin{itemize}
			\item \textbf{Automatic Recovery:} Failed tasks are retried or rescheduled transparently
			\item \textbf{Checkpointing:} Persist task execution state for efficient resumption after failures
			\item \textbf{Failure Isolation:} Failures contained to domains (clusters, partitions, workers) without cascading effects
			\item \textbf{Idempotent Operations:} Safe retries with consistent outcomes
			\item \textbf{Graceful Degradation:} Services restart without impacting running workloads
		\end{itemize}
	}

\end{frame}

\begin{frame}{Observable}
	\begin{itemize}
		\item \textbf{End-to-End Visibility:} Telemetry across scheduling, execution, and system health
		\item \textbf{Functional Observability:} Task graphs, critical paths, and execution structure
		\item \textbf{Unified View:} Correlated data across control, compute, and data domains
		\item \textbf{Business Metrics:} Domain-specific tags bridging execution and business outcomes
		\item \textbf{Intelligent Insight:} Automated anomaly detection and diagnostics
		\item \textbf{Custom Instrumentation:} User-defined metrics and tracing for domain-specific observability, also available to tasks during execution to adapt behavior based on runtime conditions
		\item \textbf{Metering \& Cost Attribution:} Per-tenant usage tracking for billing and chargeback
	\end{itemize}
\end{frame}

\begin{frame}{Malleable}
	\begin{itemize}
		\item \textbf{Elastic Resources:} Scale execution capacity up or down with workload demand
		\item \textbf{Runtime Reconfiguration:} Resize execution domains without restarts
		\item \textbf{Fixed Infrastructure:} Adjust active resource usage to avoid idle capacity
		\item \textbf{Policy-Driven:} Balance performance, cost, and fairness objectives
		\item \textbf{Predictive Adaptation:} Proactive scaling based on workload patterns
		\item \textbf{Resource Sharing:} Seamless workload distribution across environments based on resource availability and policy constraints
	\end{itemize}
\end{frame}

\begin{frame}{Portable}
	\begin{itemize}
		\item \textbf{Multi-Environment:} Cloud, on-premises, bare-metal, and supercomputing
		\item \textbf{Infrastructure-Agnostic:} Resources treated as a logical pool
		\item \textbf{Hybrid \& Multi-Cloud:} Distribute workloads across heterogeneous environments
		\item \textbf{Standards-Oriented:} Open standards to reduce ecosystem lock-in
		\item \textbf{Data Sovereignty:} Compliance-aware placement respecting residency requirements
	\end{itemize}
\end{frame}

\begin{frame}{Data Aware}
	\begin{columns}[T]
		\begin{column}{0.48\textwidth}
			\centering\vspace{0.2cm}
			\begin{tikzpicture}[
					tn/.style={rectangle, rounded corners=3pt, fill=aneoblue, text=white,
							font=\tiny\bfseries, minimum width=1.2cm, minimum height=0.45cm},
					dn/.style={circle, fill=aneoorange, text=aneoblack,
							font=\tiny\bfseries, minimum size=0.55cm},
					site/.style={draw=aneoblue!30, dashed, fill=aneoblue!5, rounded corners=4pt},
					arr/.style={-Stealth, thick},
					lab/.style={font=\tiny\itshape}
				]
				% WITHOUT
				\node[font=\tiny\bfseries, text=aneoorange] at (2.9, 0.85) {Without};
				\draw[site] (0.2, 0.05) rectangle (1.9, -0.65);
				\node[font=\tiny, text=aneoblue] at (1.05, 0.22) {Site A};
				\node[dn] (d1) at (1.05, -0.3) {D};
				\draw[site] (3.9, 0.05) rectangle (5.6, -0.65);
				\node[font=\tiny, text=aneoblue] at (4.75, 0.22) {Site B};
				\node[tn] (t1) at (4.75, -0.3) {Task};
				\draw[aneoorange, thick, -Stealth] (d1.east) -- (t1.west)
				node[midway, above, lab, text=aneoorange] {transfer};

				% DIVIDER
				\draw[aneoblack!20] (0.0, -0.85) -- (5.8, -0.85);

				% WITH
				\node[font=\tiny\bfseries, text=aneoturquoise!80!black] at (2.9, -1.1) {With};
				\draw[site] (0.2, -1.3) rectangle (2.6, -2.1);
				\node[font=\tiny, text=aneoblue] at (1.4, -1.13) {Site A};
				\node[dn] (d2) at (0.85, -1.7) {D};
				\node[tn] (t2) at (2.15, -1.7) {Task};
				\draw[arr, aneoturquoise, very thick] (d2.east) -- (t2.west)
				node[midway, above, lab, text=aneoturquoise] {local};
				\draw[site] (3.2, -1.3) rectangle (5.6, -2.1);
				\node[font=\tiny, text=aneoblue] at (4.4, -1.13) {Site B};
				\node[dn] (d3) at (3.85, -1.7) {D};
				\node[tn] (t3) at (5.15, -1.7) {Task};
				\draw[arr, aneoturquoise, very thick] (d3.east) -- (t3.west)
				node[midway, above, lab, text=aneoturquoise] {local};

				\node[font=\tiny\itshape, text=aneoblack!50] at (2.9, -2.4)
				{tasks placed where their data resides};
			\end{tikzpicture}
		\end{column}
		\begin{column}{0.52\textwidth}
			\vspace{0.4cm}
			\begin{itemize}
				\item \textbf{Data-Driven Scheduling:} Task placement accounts for data locality, dependencies, and reuse to minimize movement
				\item \textbf{Proactive Placement:} Replicate or stage data ahead of execution based on the task graph
				\item \textbf{Flexible Dependencies:} Mandatory, optional, and on-demand data classes for fine-grained scheduling
				\item \textbf{Controlled Lifecycle:} Explicit ownership, locality, and retention management
				\item \textbf{Cross-Cluster Migration:} Move data and tasks across environments for performance, cost, and compliance
			\end{itemize}
		\end{column}
	\end{columns}

	\note
	{
		\begin{itemize}
			\item \textbf{Data-Driven Scheduling:} Task placement decisions account for data locality, dependencies, and reuse to minimize data movement
			\item \textbf{Proactive Placement:} Replicate or stage data ahead of execution based on the task graph structure
			\item \textbf{Flexible Dependencies:} Mandatory, optional, and on-demand data classes enabling fine-grained scheduling trade-offs
			\item \textbf{Controlled Lifecycle:} Explicit ownership, locality, and retention management
			\item \textbf{Cross-Cluster Migration:} Move data and reschedule tasks across environments for performance, cost, and compliance
		\end{itemize}
	}

\end{frame}

\begin{frame}{Performant}
	\begin{itemize}
		\item \textbf{Low-Latency Orchestration:} Minimized coordination overhead on the critical path
		\item \textbf{Pipeline Parallelism:} Overlap data transfers and computation
		\item \textbf{High Concurrency:} Sustained throughput with large worker counts
		\item \textbf{Efficient Utilization:} Autoscaling to maximize useful work, minimize waste
		\item \textbf{Decoupled Architecture:} Loose coupling for throughput and fault isolation
	\end{itemize}
\end{frame}

\begin{frame}{Smart Scheduling}
	\centering\vspace{0.1cm}
	\begin{tikzpicture}[
			inp/.style={rectangle, rounded corners=3pt, fill=aneoblue!10,
					draw=aneoblue!30, text=aneoblack, font=\footnotesize\bfseries,
					minimum width=4.0cm, minimum height=0.6cm, align=center},
			sch/.style={rectangle, rounded corners=5pt, fill=aneoblue, text=white,
					font=\small\bfseries, minimum width=2.4cm, minimum height=4.8cm,
					align=center},
			res/.style={rectangle, rounded corners=3pt, font=\footnotesize\bfseries,
					minimum width=2.8cm, minimum height=0.65cm, align=center},
			arr/.style={-Stealth, thick, aneoblue!70}
		]
		\node[inp] (dl) at (0, 2.1)  {Data Locality};
		\node[inp] (pr) at (0, 0.7)  {Priority \& Preemption};
		\node[inp] (he) at (0,-0.7)  {Heterogeneous Compute};
		\node[inp] (dg) at (0,-2.1)  {DAG Structure};

		\node[sch] (s)  at (3.8, 0)  {ArmoniK \\ Scheduler};

		\node[res, fill=aneoturquoise!30, draw=aneoturquoise!70] (op) at (7.4, 0.9)
		{Optimal Placement};
		\node[res, fill=aneoorange!20, draw=aneoorange!60] (ca) at (7.4,-0.9)
		{Cost-Aware Scaling};

		\draw[arr] (dl.east) -- (s.west |- dl);
		\draw[arr] (pr.east) -- (s.west |- pr);
		\draw[arr] (he.east) -- (s.west |- he);
		\draw[arr] (dg.east) -- (s.west |- dg);

		\draw[-Stealth, thick, aneoturquoise!80] (s.east |- op) -- (op.west);
		\draw[-Stealth, thick, aneoorange!80]    (s.east |- ca) -- (ca.west);
	\end{tikzpicture}

	\note
	{
		\begin{itemize}
			\item \textbf{Data-Aware Placement:} Co-locate tasks with their data to reduce transfer overhead
			\item \textbf{Priority \& Preemption:} Urgent tasks preempt batch work with configurable policies
			\item \textbf{Heterogeneous Compute:} GPU, accelerator, and NUMA-aware resource matching
			\item \textbf{Pluggable Policies:} Fair-share, backfill, gang scheduling, deadline-aware
			\item \textbf{DAG Optimizations:} Critical-path scheduling, task fusion, and speculative execution
			\item \textbf{Cost-Aware Decisions:} Task duration and resource prediction inform placement and scaling
		\end{itemize}
	}
\end{frame}

% \begin{frame}{Open Source}
% 	\begin{itemize}
% 		\item \textbf{Transparency:} Inspect, audit, and understand platform behavior
% 		\item \textbf{Extensibility:} Adapt to domain-specific needs and custom integrations
% 		\item \textbf{Open Ecosystems:} Standards-based portability and long-term sustainability
% 		\item \textbf{Community-Driven:} Shared innovation, faster iteration, no vendor lock-in
% 	\end{itemize}
% \end{frame}